30June16 explant sups plate 3: MIG, RANTES, IL1ra

### 2016-07-19 30June16_plate_3_explant_sup.Rmd
updated plots

dat <- dat %>%
  filter(Sample != "Diluted Stock Calibrator" & Sample != "Blended Working Stock")
```

@@

```{r standard curves, echo=FALSE, warning=FALSE, message= FALSE}

# standardCurve<- function (Calc.Top, Calc.Bottom, Calc.HillSlope, Calc.Midpoint, Concentration){
# 
# Calc.Top + (Calc.Bottom - Calc.Top/(1+(Concentration/Calc.Midpoint)^Calc.HillSlope))
# }
# 
# 
# MIGcurveData <- standards%>%
#   filter(Assay == "MIG") %>%
#   mutate(UpperLimit = Algorithm.Parameter..Calc..Top-( Detection.Limits..Top.of.Range.Parameter * Std..Deviation ))%>%
#   mutate(LowerLimit = min(Concentration)+(2.5 * Std..Deviation ))
# 
# 
# 
# MIGcalcCurve <- standardCurve(MIGcurveData$Algorithm.Parameter..Calc..Top,MIGcurveData$Algorithm.Parameter..Calc..Bottom, MIGcurveData$Algorithm.Parameter..Calc..HillSlope, MIGcurveData$Algorithm.Parameter..Calc..MidPoint, MIGcurveData$Concentration)
# 
# 
# ggplot(MIGcurveData, aes(x = Concentration, y = Signal))+
#   geom_point()+
#   scale_y_log10()+
#   scale_x_log10()+
#   geom_line(aes(y = MIGcalcCurve))+
#   geom_hline(yintercept = MIGcurveData$UpperLimit)

@@

```{r everything, echo=FALSE, warning=FALSE, message= FALSE}

@@

>>>>

dat <- dat %>%
  filter(Sample != "Diluted Stock Calibrator" & Sample != "Blended Working Stock")

@@

```{r standard curves, echo=FALSE, warning=FALSE, message= FALSE}
#according to MSD instructions, the lower detection limit for the standards (in signal units) is the signal for the lower calibrator + (statistical factor * multiplier)

# upper limit is calculated this way: upper plateau of standard curve - (multiplier x statistical factor). The upper plateau value is in the "Algorithm Parameter Calc Top" column.

#the statistical factor used can be found in the "Detection limits bottom of range type" column and the multiplier can  be found in the "Detection limits bottom of range parameter" column

#for the 4PL curve, std deviation is the statistical factor used for both limits.

# LowerLimits <-standards %>%
#   group_by(Assay)%>%
#   filter(Sample == "STD-08")%>%
#   summarize(LowerLimit = unique(Mean + (Std..Deviation * Detection.Limits..Bottom.of.Range.Parameter)))
# 
# UpperLimits<- standards %>%
#   group_by(Assay)%>%
#   summarise(UpperLimit = unique(Algorithm.Parameter..Calc..Top - (Std..Deviation * Detection.Limits..Top.of.Range.Parameter)))
# 
# standards<-merge(standards,LowerLimits, by = "Assay")
# 
# standards<- merge(standards, UpperLimits, by = "Assay")
# 
# 
# 
# MIGstandards<- filter(standards, Assay == "MIG")
# 
# MIGstandards%>%
#   ggplot(aes(x = Concentration, y = Signal))+
#   geom_point()+
#   scale_y_log10()+
#   scale_x_log10()+
#   geom_hline(yintercept = MIGstandards$UpperLimit[1])+
#   geom_hline(yintercept = MIGstandards$LowerLimit[1])+
#   ggtitle("MIG")
#   
# 
# RANTESstandards<- filter(standards, Assay == "RANTES")
# 
# RANTESstandards%>%
#   filter(Assay == "RANTES")%>%
#   ggplot(aes(x = Concentration, y = Signal))+
#   geom_point()+
#   scale_y_log10()+
#   scale_x_log10()+
#   geom_hline(yintercept = RANTESstandards$UpperLimit[1])+
#   geom_hline(yintercept = RANTESstandards$LowerLimit[1])+
#   ggtitle("RANTES")
# 
# IL1RAstandards<-filter(standards, Assay == "IL1-RA")
# 
# IL1RAstandards%>%
#   filter(Assay == "IL1-RA")%>%
#   ggplot(aes(x = Concentration, y = Signal))+
#   geom_point()+
#   scale_y_log10()+
#   scale_x_log10()+
#   geom_hline(yintercept = IL1RAstandards$UpperLimit[1])+
#   geom_hline(yintercept = IL1RAstandards$LowerLimit[1])+
#   ggtitle("IL1-RA")

@@

```{r all analytes, echo=FALSE, warning=FALSE, message= FALSE}

@@

When we analyzed the explant microarray data, we saw the most obvious differences in gene expression were in V2T3 for donors 323,317,324,318. The only sample that was in this subset that we ran on this plate was 323.

```{r subset, echo=FALSE, warning=FALSE, message= FALSE}
subset <- explantDat %>%
  filter(Donor!="319" & Donor != "319" & Donor != "327" & Donor!= "326", Timepoint == "T3")

ggplot(subset, aes(x = Virus, y = Calc..Concentration))+

  theme(axis.text.x = element_text(angle = 25, size = 9))

Data separated by analyte:
